Component response rate variation drives stability in large complex systems

### 2018-04-20 ms.Rmd
Figure 3 stuff

>>>>

**Figure 3: Stability of large complex systems with and without variation in component response rate ($\boldsymbol{\gamma}$).** Panels show the $\ln$ number of systems that are stable across different system sizes ($S$) given $C = 1$, and the proportion of systems in which variation in $\gamma$ is critical for system stability. For each $S$, 1 million complex systems are randomly generated and tested for stability before and after variation in $\gamma$ is included at four different distributions: **a**, uniform, **b**, exponential, **c**, beta, and **d**, gamma. Red and black bars show the number of stable systems in the absence and presence of variance in $\gamma$, respectively. Blue lines show the proportion of systems that are stable when $Var(\gamma) > 0$, but would be unstable if $Var(\gamma) = 0$.

```{r, eval = TRUE, echo = FALSE, fig.height = 8}
dat <- read.csv(file = "sim_results/C_1/random_all.csv");
stable_N_plot(dat);
```
